DATA DRIVEN MODELS FOR APOGEE M DWARFS

### 2018-03-30 paper/draft1/draft1.tex
add affil

\shorttitle{Birky \& Hogg}
\shortauthors{Birky \& Hogg}

@@

@@

\begin{enumerate}
\item[-] We trained The Cannon on 51 M dwarfs with a one-dimensional spectral type label, and was able to achieve a precision of $\pm$0.8 spectral types, more precise than the original training label uncertainty of $\pm$1 spectral type.
\item[-] Two tests of consistency were used to assess the validity of our derived test labels: Figure \ref{fig:west_selftest} displays the label self-test for the spectral type model, and Figure 2 displays 
\end{enumerate}

>>>>

\shorttitle{Birky et al.}
\shortauthors{Birky et al.}

@@

\author[0000-0003-3654-1602]{Andrew Mann}
\affil{Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA}

@@

\begin{enumerate}
\item[-] We trained The Cannon on 51 M dwarfs with a one-dimensional spectral type label, and obtained a precision of $\pm$0.8 spectral types, more precise than the original training label uncertainty of $\pm$1 spectral type.
\item[-] Two tests of consistency were used to assess the validity of our derived test labels: Figure \ref{fig:west_selftest} displays the label self-test for the spectral type model, and Figure  displays 
\end{enumerate}
